Lesson 5
========================================================

```{r}
# setwd for Home workstation
setwd("C:/Users/Mahlon/Source/Repos/DAND-P4-Explore-and-Summarize-Data/EDA_Course_Materials/lesson5")

# setwd for Work workstation
setwd("C:/Source (Remote)/Repos/DAND-P4-Explore-and-Summarize-Data/EDA_Course_Materials/lesson5")

load('.rdata')

library(ggplot2)
library(tidyr)
library(dplyr)
library(xlsx)
library(lubridate)
library(gridExtra)
```

### Multivariate Data
Notes:

***

### Moira Perceived Audience Size Colored by Age
Notes:
Adding color to represent age was a deadend. This is common in EDA
***

### Third Qualitative Variable
Notes:

```{r Third Qualitative Variable}
pf <- read.delim("../datasets/pseudo_facebook.tsv")
ggplot(aes(x = gender, y = age),
       data = subset(pf, !is.na(gender))) + geom_histogram()

ggplot(aes(x = gender, y = age),
       data = subset(pf, !is.na(gender))) + geom_boxplot() +
  stat_summary(fun.y = mean, geom = 'point', shape = 4)

ggplot(aes(x = age, y = friend_count),
       data = subset(pf, !is.na(gender))) +
  geom_line(aes(color = gender), stat = "summary", fun.y = median)
```

***

### Plotting Conditional Summaries
Notes:

```{r Plotting Conditional Summaries}
pf.fc_by_age_gender <- pf %>% 
                       filter(!is.na(gender)) %>%
                       group_by(age, gender) %>% 
                       summarize(mean_friend_count = mean(friend_count),
                                 median_friend_count = median(friend_count),
                                 n = n()) %>% 
                       ungroup() %>% 
                       arrange(age)

ggplot(aes(x = age, y = median_friend_count),
           data = pf.fc_by_age_gender) +
  geom_line(color = gender)
```

***

### Thinking in Ratios
Notes:

***

### Wide and Long Format
Notes:

***

### Reshaping Data
Notes:

```{r}
install.packages('reshape2')
library(reshape2)
pf.fc_by_age_gender.wide = dcast(pf.fc_by_age_gender,
                                 age ~ gender,
                                 value.var = 'median_friend_count')

pf.fc_by_age_gender.long = melt(pf.fc_by_age_gender.wide, id.vars = c("age"),
                                variable.name = 'gender',
                                value.name = 'median_friend_count')
```


***

### Ratio Plot
Notes:

```{r Ratio Plot}
ggplot(aes(y = female / male, x = age), data =  pf.fc_by_age_gender.wide) +
  geom_line() +
  geom_hline(yintercept = 1, linetype = 2, alpha = 0.3)
```

***

### Third Quantitative Variable
Notes:

```{r Third Quantitative Variable}
pf$year_joined <- floor(2014 - (pf$tenure / 365))
head(pf)
```

***

### Cut a Variable
Notes:

```{r Cut a Variable}
pf$year_joined.bucket <- cut(pf$year_joined, c(2004,2009, 2011, 2012,2014))
```

***

### Plotting it All Together
Notes:

```{r Plotting it All Together}
table(pf$year_joined.bucket)

ggplot(aes(x = age,  y = friend_count), data = subset(pf, !is.na(gender))) +
  geom_line(aes(color = gender), stat = 'summary', fun.y = median)

ggplot(aes(x = age,  y = friend_count), data = subset(pf, !is.na(gender))) +
  geom_line(aes(color = year_joined.bucket), stat = 'summary', fun.y = median)
```

***

### Plot the Grand Mean
Notes:

```{r Plot the Grand Mean}
ggplot(aes(x = age,  y = friend_count), 
       data = subset(pf, !is.na(gender)| !is.na(year_joined.bucket))) +
  geom_line(aes(color = year_joined.bucket), stat = 'summary', fun.y = mean) +
  geom_line(stat = 'summary', fun.y = mean, linetype = 2)
```

***

### Friending Rate
Notes:

```{r Friending Rate}
pf$mfr <- pf$friend_count / ifelse(pf$tenure < 1, 1, pf$tenure)

# Instructor code is better :D
with(subset(pf, tenure >= 1), summary(friend_count / tenure))
```

***

### Friendships Initiated
Notes:

What is the median friend rate?
0.2202

What is the maximum friend rate?
417
```{r Friendships Initiated}
ggplot(aes(x = friendships_initiated / tenure,  y = tenure),
       data = subset(pf, tenure >= 1 & !is.na(gender) | 
                     !is.na(year_joined.bucket))) +
  geom_line(aes(color = gender), stat = 'summary', fun.y = median)
```

***

### Bias-Variance Tradeoff Revisited
Notes:

```{r Bias-Variance Tradeoff Revisited}

ggplot(aes(x = tenure, y = friendships_initiated / tenure),
       data = subset(pf, tenure >= 1)) +
  geom_line(aes(color = year_joined.bucket),
            stat = 'summary',
            fun.y = mean)

ggplot(aes(x = 7 * round(tenure / 7), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

ggplot(aes(x = 30 * round(tenure / 30), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

ggplot(aes(x = 90 * round(tenure / 90), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

```

***

### Sean's NFL Fan Sentiment Study
Notes:

***

### Introducing the Yogurt Data Set
Notes:

***

### Histograms Revisited
Notes:

```{r Histograms Revisited}

```

***

### Number of Purchases
Notes:

```{r Number of Purchases}

```

***

### Prices over Time
Notes:

```{r Prices over Time}

```

***

### Sampling Observations
Notes:

***

### Looking at Samples of Households

```{r Looking at Sample of Households}

```

***

### The Limits of Cross Sectional Data
Notes:

***

### Many Variables
Notes:

***

### Scatterplot Matrix
Notes:

***

### Even More Variables
Notes:

***

### Heat Maps
Notes:

```{r}
nci <- read.table("nci.tsv")
colnames(nci) <- c(1:64)
```

```{r}
nci.long.samp <- melt(as.matrix(nci[1:200,]))
names(nci.long.samp) <- c("gene", "case", "value")
head(nci.long.samp)

ggplot(aes(y = gene, x = case, fill = value),
  data = nci.long.samp) +
  geom_tile() +
  scale_fill_gradientn(colours = colorRampPalette(c("blue", "red"))(100))
```


***

### Analyzing Three of More Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

