Lesson 4
========================================================

***

### Scatterplots and Perceived Audience Size
Notes:

***

### Scatterplots
Notes:

```{r Scatterplots}
pf <- read.delim('../datasets/pseudo_facebook.tsv')
pf
qplot(x = age, y = friend_count, data = pf)
```

***

#### What are some things that you notice right away?
Response:
Younger users tend to have more friends. There are more younger users. There are some very distinct vertical bands at some ages > 60.
***

### ggplot Syntax
Notes:

```{r ggplot Syntax}
ggplot(aes(x = age, y = friend_count), data = pf) +
  geom_point() +
  xlim(13, 90)
```

***

### Overplotting
Notes:

```{r Overplotting}
ggplot(aes(x = age, y = friend_count), data = pf) +
  geom_point(alpha = 1/20) +
  xlim(13, 90)

ggplot(aes(x = age, y = friend_count), data = pf) +
  geom_jitter(alpha = 1/20) +
  xlim(13, 90)
```

#### What do you notice in the plot?
Response:

***

### Coord_trans()
Notes:

```{r Coord_trans()}

ggplot(aes(x = age, y = friend_count), data = subset(pf, friend_count > 0 || age > 0)) +
  geom_jitter(alpha = 1/20) +
  xlim(13, 90)
```

#### Look up the documentation for coord_trans() and add a layer to the plot that transforms friend_count using the square root function. Create your plot!

```{r}
# geom_jitter() introduces noise (+ and -) that could create values that would be imaginary when passed to sqrt
?coord_trans
ggplot(aes(x = age, y = friend_count), data = subset(pf, friend_count > 0 || age > 0)) +
  geom_point(alpha = 1/20, position = position_jitter(h = 0)) +
  xlim(13, 90) +
  coord_trans(y = "sqrt")

ggplot(aes(x = age, y = friend_count), data = subset(pf, friend_count > 0 || age > 0)) +
  geom_point(alpha = 1/20) +
  xlim(13, 90) +
  coord_trans(y = "sqrt")
```

#### What do you notice?

***

### Alpha and Jitter
Notes:

```{r Alpha and Jitter}
ggplot(aes(x = age, y = friendships_initiated), data = pf) +
  geom_point(alpha = 1/20, position = position_jitter(h = 0)) +
  scale_x_continuous(limits = c(13,90), breaks = seq(13, 90, 2)) +
  coord_trans(y = "sqrt")
```

***

### Overplotting and Domain Knowledge
Notes:

***

### Conditional Means
Notes:

```{r Conditional Means}
library(dplyr)

pf.fc_by_age <- group_by(pf, age) %>%
                summarise(friend_count_mean = mean(friend_count),
                          friend_count_median = median(friend_count),
                          n = n()) %>% 
                arrange(age)
head(pf.fc_by_age)
```

Create your plot!

```{r Conditional Means Plot}
ggplot(aes(y = friend_count_mean, x = age), data = pf.fc_by_age) +
  geom_line()

ggplot(aes(y = friend_count_median, x = age), data = pf.fc_by_age) +
  geom_line()
```

***

### Overlaying Summaries with Raw Data
Notes:

```{r Overlaying Summaries with Raw Data}
ggplot(aes(x = age, y = friend_count), data = pf) +
  geom_point(alpha = 1/20, 
             position = position_jitter(h = 0), 
             color = 'orange') +
  
  geom_line(stat = "summary", fun.y = mean) +
  geom_line(stat = "summary", fun.y = quantile, 
            fun.args = list(probs = 0.1),
            linetype = 2, color = 'blue') +
  geom_line(stat = "summary", fun.y = quantile, 
            fun.args = list(probs = 0.5),
            linetype = 2, color = 'blue') +
  geom_line(stat = "summary", fun.y = quantile, 
            fun.args = list(probs = 0.9),
            linetype = 2, color = 'blue') +
  coord_cartesian(xlim = c(13,70), ylim = c(0, 1000) )

#coord_trans(y = "sqrt") +
#scale_x_continuous(limits = c(13,90), breaks = seq(13, 90, 2)) +
  
```

#### What are some of your observations of the plot?
Response:
1000 friends is rare. Adults tend to have around 100 friends.

***

### Moira: Histogram Summary and Scatterplot
See the Instructor Notes of this video to download Moira's paper on perceived audience size and to see the final plot.

Notes:

***

### Correlation
Notes:

```{r Correlation}
?cor.test
cor.test(pf$age, pf$friend_count)
with(pf, cor.test(age, friend_count))
```

Look up the documentation for the cor.test function.

What's the correlation between age and friend count? Round to three decimal places.
Response:

***

### Correlation on Subsets
Notes:

```{r Correlation on Subsets}
with(subset(pf, age <= 70), cor.test(age, friend_count))
```

***

### Correlation Methods
Notes:

***

## Create Scatterplots
Notes:

```{r}
with(pf, qplot(likes_received, www_likes_received))

ggplot(aes(x = log10(www_likes_received), y = log10(likes_received)), data = pf) +
  geom_point(alpha = 1/40, position = position_jitter(h = 0)) +
  scale_x_log10() +
  scale_y_log10() +
  coord_trans(x = 'log10', y = 'log10')
```

***

### Strong Correlations
Notes:

```{r Strong Correlations}
ggplot(aes(x = www_likes_received, y = likes_received), data = pf) +
  geom_point(alpha = 1/40, position = position_jitter(h = 0)) +
  xlim(0, quantile(pf$www_likes_received, 0.95)) +
  ylim(0, quantile(pf$likes_received, 0.95))+
  geom_smooth(method = 'lm', color = 'red')
```

What's the correlation betwen the two variables? Include the top 5% of values for the variable in the calculation and round to 3 decimal places.

```{r Correlation Calcuation}
with(pf, cor.test(likes_received, www_likes_received))
```

Response:

***

### Moira on Correlation
Notes:

***

### More Caution with Correlation
Notes:

```{r More Caution With Correlation}
install.packages('alr3')
library(alr3)
data(Mitchell)
head(Mitchell)
```

Create your plot!

```{r Temp vs Month}
ggplot(aes(x = Month, y = Temp), data = Mitchell) +
  geom_point()
```

***

### Noisy Scatterplots
a. Take a guess for the correlation coefficient for the scatterplot.

b. What is the actual correlation of the two variables?
(Round to the thousandths place)

```{r Noisy Scatterplots}
with(Mitchell, cor.test(Month, Temp))
```

***

### Making Sense of Data
Notes:

```{r Making Sense of Data}
# cyclical pattern
ggplot(aes(x = Month, y = Temp), data = Mitchell) +
  geom_point() +
  scale_x_discrete(breaks = seq(0, 200, 12))

ggplot(aes(x=(Month%%12),y=Temp),data=Mitchell)+ 
  geom_point()

install.packages('energy')
library(energy)

x <- seq(0, 4*pi, pi/20)
y <- cos(x)
qplot(x = x, y = y)
energy::dcor.ttest(x, y)
```

***

### A New Perspective

What do you notice?
Response:
Cyclical pattern
Watch the solution video and check out the Instructor Notes!
Notes:
Perspective and scale are very important with data visualization
***

### Understanding Noise: Age to Age Months
Notes:

```{r Understanding Noise: Age to Age Months}

pf$age_with_months = pf$age + (1 - (pf$dob_month / 12)) # or

pf$age_with_months = pf$age + ((12 - pf$dob_month) / 12)

```

***

### Age with Months Means

```{r Age with Months Means}
library(dplyr)

pf.fc_by_age_months <- group_by(pf, age_with_months) %>%
                summarise(friend_count_mean = mean(friend_count),
                          friend_count_median = median(friend_count),
                          n = n()) %>% 
                arrange(age_with_months)
head(pf.fc_by_age_months)

ggplot(aes(y = friend_count_mean, x = age_with_months), data = pf.fc_by_age_months) +
  geom_line()

ggplot(aes(y = friend_count_median, x = age_with_months), data = pf.fc_by_age_months) +
  geom_line()

ggplot(aes(y = friend_count_median, x = age_with_months), data = subset(pf.fc_by_age_months, age_with_months < 71)) +
  geom_point()

ggplot(aes(y = friend_count_median, x = age_with_months), data = subset(pf.fc_by_age_months, age_with_months < 71)) +
  geom_line()

```

Programming Assignment
```{r Programming Assignment}

```

***

### Noise in Conditional Means

```{r Noise in Conditional Means}

```

***

### Smoothing Conditional Means
Notes:

```{r Smoothing Conditional Means}

```

***

### Which Plot to Choose?
Notes:

***

### Analyzing Two Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

