---
title: "EDA of Red Wine Quality Data"
author: "Mahlon Barrault"
date: "December 14, 2016"
output: html_document
---
========================================================

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
# Load all of the packages that you end up using
# in your analysis in this code chunk.

# Notice that the parameter "echo" was set to FALSE for this code chunk.
# This prevents the code from displaying in the knitted HTML output.
# You should set echo=FALSE for all code chunks in your file.

library(ggplot2)
library(dplyr)
library(tidyr)
```

```{r echo=FALSE, Load_the_Data}
# Load the Data
wine_quality <- read.csv("../Data/wineQualityReds.csv")
```

# Univariate Plots Section
```{r echo=TRUE, Univariate_Plots}
str(wine_quality)
summary(wine_quality)
```
I think it might be useful to have quality as a factor

```{r echo=TRUE, Univariate_Plots}
wine_quality$quality <- factor(ordered(wine_quality$quality))
str(wine_quality$quality)
summary(wine_quality$quality)
```

Now that I am happy with how quality is looking lets see what it looks like

```{r echo=FALSE, Univariate_Plots}
ggplot(data = wine_quality, aes(x = quality)) + geom_bar(stat = "count") 
```
No scores of less than 3. Scores of 3 and 4 are uncommon. 5 or better represents the bulk of the wines.
After seeing the distribution of quality I wanted to check the mean and standard deviation. It was a little tricky after converting quality to a factor.

```{r echo=TRUE, Univariate_Plots}
qual_mean <- mean(as.numeric(levels(wine_quality$quality)[wine_quality$quality]))
qual_sd <- sd(as.numeric(levels(wine_quality$quality)[wine_quality$quality]))
qual_mean
qual_sd
```
The mean and standard deviation look approriate for this distribution

Now let's look at some of the other variables that could contribute to the quality rating

Let's see what the variables related to acidity look like

```{r echo=FALSE, Univariate_Plots}
ggplot(data = wine_quality, aes(x = fixed.acidity)) + geom_histogram(binwidth = 0.2) 
```

```{r echo=FALSE, Univariate_Plots}
ggplot(data = wine_quality, aes(x = volatile.acidity)) + geom_histogram(binwidth = 0.03) 
```

```{r echo=FALSE, Univariate_Plots}
ggplot(data = wine_quality, aes(x = citric.acid)) + geom_histogram(binwidth = 0.02) 
```

```{r echo=FALSE, Univariate_Plots}
ggplot(data = wine_quality, aes(x = citric.acid)) + geom_histogram(binwidth = 0.01) 
```

Several wines have 0.00 g/L citric acid. There is an interesting spike of wines with 0.49 g/L citric acid. I will have a closer look at that later.

```{r echo=TRUE, Univariate_Plots}
#wine_quality$citric.acid
cond <- wine_quality$citric.acid == 0.49
wine_quality[cond,]
```

```{r echo=FALSE, Univariate_Plots}
ggplot(data = wine_quality, aes(x = pH)) + geom_histogram(binwidth = 0.02) 
```

Most wines in this data set fall between 3.1 and 3.5

Now let's see what the variables for sulphates content look like

```{r echo=FALSE, Univariate_Plots}
ggplot(data = wine_quality, aes(x = free.sulfur.dioxide)) + geom_histogram(binwidth = 1) 
```

```{r echo=FALSE, Univariate_Plots}
ggplot(data = wine_quality, aes(x = total.sulfur.dioxide)) + geom_histogram(binwidth = 3) 
```

```{r echo=FALSE, Univariate_Plots}
ggplot(data = wine_quality, aes(x = sulphates)) + geom_histogram(binwidth = 0.02) 
```

All of the sulphate variables seem to have a simular right skew. There seem to be some wines with very high sulphate content relative to the rest of the wines.

# Univariate Analysis

### What is the structure of your dataset?

### What is/are the main feature(s) of interest in your dataset?

### What other features in the dataset do you think will help support your investigation into your feature(s) of interest?

### Did you create any new variables from existing variables in the dataset?

### Of the features you investigated, were there any unusual distributions? Did you perform any operations on the data to tidy, adjust, or change the form of the data? If so, why did you do this?



# Bivariate Plots Section
```{r echo=FALSE, Bivariate_Plots}

```

# Bivariate Analysis

### Talk about some of the relationships you observed in this part of the investigation. How did the feature(s) of interest vary with other features in the dataset?

### Did you observe any interesting relationships between the other features (not the main feature(s) of interest)?

### What was the strongest relationship you found?




# Multivariate Plots Section

```{r echo=FALSE, Multivariate_Plots}

```

# Multivariate Analysis

### Talk about some of the relationships you observed in this part of the investigation. Were there features that strengthened each other in terms of looking at your feature(s) of interest?

### Were there any interesting or surprising interactions between features?

### OPTIONAL: Did you create any models with your dataset? Discuss the strengths and limitations of your model.

------

# Final Plots and Summary

### Plot One
```{r echo=FALSE, Plot_One}

```

### Description One


### Plot Two
```{r echo=FALSE, Plot_Two}

```

### Description Two


### Plot Three
```{r echo=FALSE, Plot_Three}

```

### Description Three

------

# Reflection
