---
title: "EDA of Red Wine Quality Data"
author: "Mahlon Barrault"
date: "December 14, 2016"
output: html_document
---
========================================================

```{r setup, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
# Load all of the packages that you end up using
# in your analysis in this code chunk.

# Notice that the parameter "echo" was set to FALSE for this code chunk.
# This prevents the code from displaying in the knitted HTML output.
# You should set echo=FALSE for all code chunks in your file.

library(ggplot2)
library(dplyr)
library(tidyr)
library(lubridate)
library(gridExtra)
library(GGally)
library(reshape2)
library(RColorBrewer)
library(scales)
library(memisc)

# Load the Data
wine_quality <- read.csv("../Data/wineQualityReds.csv")

```

# Univariate Plots Section
```{r echo=TRUE, Univariate_Plots1}
summary(wine_quality)
```

I think it might be useful to have quality as a factor

```{r echo=TRUE, Univariate_Plots2}
wine_quality$quality <- factor(ordered(wine_quality$quality))
str(wine_quality$quality)
summary(wine_quality$quality)
```

Now that I am happy with how quality is looking lets see what it looks like

```{r echo=FALSE, Univariate_Plots3}
ggplot(data = wine_quality, aes(x = quality)) + 
  geom_bar(stat = "count") 
```

No scores of less than 3. Scores of 3 and 4 are uncommon. 5 or better represents the bulk of the wines.
After seeing the distribution of quality I wanted to check the mean and standard deviation. It was a little tricky after converting quality to a factor.

```{r echo=TRUE, Univariate_Plots4}
qual_mean <- mean(as.numeric(levels(wine_quality$quality)[wine_quality$quality]))
qual_sd <- sd(as.numeric(levels(wine_quality$quality)[wine_quality$quality]))
qual_mean
qual_sd
```

The mean and standard deviation look appropriate for this distribution

Now let's look at some of the other variables that could contribute to the quality rating

Let's see what the variables related to acidity look like.

For single variable analysis I prefer the density plot since you don't have to be overly concerned tweaking the binwidth.

```{r echo=FALSE, Univariate_Plots5}
ggplot(data = wine_quality, aes(x = fixed.acidity)) + 
  geom_density()
```

```{r echo=FALSE, Univariate_Plots6}
ggplot(data = wine_quality, aes(x = volatile.acidity)) + 
  geom_density()
```

There could be a bimodal distribution happening here with volatile.acidity.

Now for citric.acid

```{r echo=FALSE, Univariate_Plots7}
ggplot(data = wine_quality, aes(x = citric.acid)) + geom_density()
ggplot(data = wine_quality, aes(x = citric.acid)) + geom_histogram(binwidth = 0.01)
```

Several wines have 0.00 g/L citric acid. The density plot is a is a little hard to tell where the bulk of these data are. The histogram doesn't really help the situation. citric.acid distribution has elements of a uniform distribution. There is an interesting spike of wines with 0.24 and 0.49 g/L citric acid. I wonder if these could additional modes could indicate wine from a specific producer. 

```{r echo=FALSE, Univariate_Plots8}
# http://mgimond.github.io/ES218/Week05a.html
ggplot(wine_quality, aes(x=1, y=citric.acid)) + 
  geom_boxplot() +
  xlab(NULL) + 
  theme(axis.text.y=element_blank()) + 
  coord_flip() +
  scale_y_continuous(limits = c(0, 1.1), breaks = seq(0, 1.1, 0.1))
```

This plot sheds a bit of light on where the majority of the citric.acid observations are. Looks like about half of the observations are between 0.1 and 0.4 g\L.

Let's take a look at pH

```{r echo=FALSE, Univariate_Plots9}
ggplot(data = wine_quality, aes(x = pH)) + 
  geom_density()
```

Most wines in this data set fall between 3.1 and 3.5

Now let's see what the variables for sulphate and related compounds content looks like

```{r echo=FALSE, Univariate_Plots10}
ggplot(data = wine_quality, aes(x = free.sulfur.dioxide)) + 
  geom_density()

ggplot(data = wine_quality, aes(x = log(free.sulfur.dioxide))) + 
  geom_density()
```

```{r echo=FALSE, Univariate_Plots11}
ggplot(data = wine_quality, aes(x = total.sulfur.dioxide)) + 
  geom_density()

ggplot(data = wine_quality, aes(x = log(total.sulfur.dioxide))) + 
  geom_density()
```

```{r echo=FALSE, Univariate_Plots12}
ggplot(data = wine_quality, aes(x = sulphates)) + 
  geom_density()

ggplot(data = wine_quality, aes(x = log(sulphates))) + 
  geom_density()
```

All of the sulphate variables seem to have a similar right skew. There seem to be some wines with very high sulphate content relative to the rest of the wines.

Finally let's see what alcohol and related parameters looks like:

```{r echo=FALSE, Univariate_Plots13}
ggplot(data = wine_quality, aes(x = alcohol)) + 
  geom_density()
```

Most wines have between 9% and 11% ABV

```{r echo=FALSE}
# http://mgimond.github.io/ES218/Week05a.html
ggplot(wine_quality, aes(x=1, y=alcohol)) + 
  geom_boxplot() +
  xlab(NULL) + 
  theme(axis.text.y=element_blank()) + 
  coord_flip() +
  scale_y_continuous(limits = c(8, 15), breaks = seq(8, 15))
```

Half of the observations are between 9.5% to 11.1% ABV

```{r echo=FALSE, Univariate_Plots14}
ggplot(data = wine_quality, aes(x = density)) + 
  geom_density()
```

No surprises here. 

```{r echo=FALSE, Univariate_Plots15}
ggplot(aes(x = residual.sugar), data = wine_quality) + 
  geom_density()

ggplot(aes(x = log(residual.sugar)), data = wine_quality) + 
  geom_density()
```

Most of the wines sampled have around 2 g/L residual.sugar. Plotting the log transformation of this variable inidcates possible lognormal distribution of the variable. 

There are some wines with very high residual sugars; let's zoom in on the mean:

```{r echo=FALSE, Univariate_Plots16}
ggplot(aes(x = residual.sugar), data = wine_quality) + 
  geom_density() + 
  scale_x_continuous(limits = c(0, 6))
```

Seems like most of the values are between 1.5 and 2.5.
There seems to be areas of increased frequency at 4 and 5 out on the tail.

```{r echo=FALSE, Univariate_Plots17}
ggplot(aes(x = residual.sugar), data = wine_quality) + 
  geom_density() + 
  scale_x_continuous(limits = c(3, 7))
```

There seemed to be some secondary modes in the original plot, however I think all I was noticing places where there sparse values making it seem like an additional peak.

```{r echo=FALSE, Univariate_Plots18}
# http://mgimond.github.io/ES218/Week05a.html
ggplot(wine_quality, aes(x=1, y=residual.sugar)) + 
  geom_boxplot() +
  xlab(NULL) + 
  theme(axis.text.y=element_blank()) + 
  coord_flip() +
  scale_y_continuous(limits = c(0, 17), breaks = c(0:17))
```

Box plot confirms what I was seeing in the density plot - most of the falling in a narrow lower band around the median with some widely spaced outliers.

Looks like most of the red wine sampled fell in the 9% to 11% ABV range. Alcohol volumes of 9.5% and 10.9% seem to more common. The plot of the density variable looks almost too perfectly normally distributed. It does make sense since there aren't many wines with a very high alcohol content or very high residual sugars. I was expecting the alcohol and residual sugar plots to appear very similar. The relationship between these two variables must be more complex than I expected.

Last but not least - chlorides. This physiochemical measurement didn't fall in to any of the other logical groupings so it has been plotted on it's own.

```{r echo=FALSE, Univariate_Plots19}
ggplot(aes(x = chlorides), data = wine_quality) + 
  geom_density()

ggplot(aes(x = log(chlorides)), data = wine_quality) + 
  geom_density()
```

Very high right skew here possibly indicating a lognormal distribution. Plotting log transformed chlorides seems to confirm that. Very few observations outside of the 0.05 to 0.15 range.

# Univariate Analysis

### What is the structure of your dataset?
```{r}
str(wine_quality)
```
There are 1599 red wines in this data set each with measurements of 11 of their physio-chemical properties and a sensory measurement of quality. The quality variable is the median of at least 3 taste tests by wine experts. I have chosen to make quality and ordered factor to reflect the specification the researchers used when collecting these data - the higher the number, the better the wine.

### What is/are the main feature(s) of interest in your dataset?
The data set has several related groups of variables. With a view to predicting a quality rating one might consider the primary flavor or aromatic factors such as acidity (fixed.acidity, volatile.acidity, citric.acid) or sweetness (residual.sugars). The data set provides other measurements of interest. I am particularly interested in discovering if the group of variables for amounts of sulfur containing compounds (free.sulfur.dioxide, total.sulfur.dioxide, sulphates) has any effect on the quality score.

### What other features in the dataset do you think will help support your investigation into your feature(s) of interest?
I suspect that there might be multicolinearity in this data since often times the presence of higher acidity or sugars can alter ones perception of other compounds. I plan to investigate the how acidity and higher sugar content work in conjunction with the sulfur containing compound to effect the quality rating.

### Did you create any new variables from existing variables in the dataset?
Most of the variables in this data set seemed to be valuable on their own and there wasn't any clear way to combine any of them in a meaningful way. One alteration I did make was to convert the quality variable in to a factor for easier analysis.

### Of the features you investigated, were there any unusual distributions? Did you perform any operations on the data to tidy, adjust, or change the form of the data? If so, why did you do this?
Some of the distributions were unexpected but not bizarre in any way.


# Bivariate Plots Section

What are the driving corellations?

```{r echo=TRUE, Bivariate_Plots0}
# https://briatte.github.io/ggcorr/
wq <- wine_quality[, !(names(wine_quality) %in% c("X"))]
wq$quality <- as.numeric(levels(wq$quality)[wq$quality])
wq.cor <- cor(wq)
data.frame(wq.cor)
# Using default continuous color map
ggcorr(wq, label = TRUE, hjust = 0.9, layout.exp = 2)
# Using default descrete color map
ggcorr(wq, nbreaks = 3, label = TRUE, hjust = 0.9, layout.exp = 2)
```

Seeing this correllation plot I am curious if the taste testers were aware of the wine's alcohol content during tasting. If so, I would be concerned that this is a source of bias in these data. The alcohol variable seems to explain about substantial amount of the variance in the quality variable. volatile.acidity has fairly high negative correllation to the quality variable. Not surprised about that. Aceitic acid vapor is not what most people are looking for when they take the first sip. I am curious about the slightly elevated correllation of sulphates and the quality variable. Despite being evident during the univariate exploration, I am still a little surprised by the 0 values for residual.sugar for alcohol and quality.

```{r echo=TRUE, Bivariate_Plots1}
ggplot(wine_quality, aes(x = quality, y = alcohol)) +
  geom_jitter(alpha = 1/10)
```

Tried several alpha values and jitter. There seems to be a lower mean when quality is 5 but a scatter plot with a factor makes things a little unclear. Probably better as box plot I am thinking.

```{r echo=TRUE, Bivariate_Plots2}
# http://stackoverflow.com/questions/3989987/joining-means-on-a-boxplot-with-a-line-ggplot2
ggplot(wine_quality, aes(x = quality, y = alcohol)) +
  geom_boxplot() +
  # aes(group = 1) added to line plot forces stat_summary to be scoped to pre-aggregated data so line can connect means from each group
  stat_summary(aes(group = 1), fun.y = mean, geom = "line", show.legend = FALSE) +
  stat_summary(fun.y = mean, geom = "point", shape = "µ", size = 2, show.legend = FALSE) 
```

That's better. With the box plot you can the trend from the scatter plot more clearly. Most of the lower scores tend to have an alcohol content around 10. Scores of 5 are densly packed around the median with several outliers, some of which are extreme. Starting with scores of 6 and above there seems to be an upward trend in the mean alcohol content. To keep this in prespective I want to remind myself how many observations fall in to each of the scores. Adding the mean marker m and a connecting line makes the tendancy in these data clearer.

```{r echo=TRUE, Bivariate_Plots3}
summary(wine_quality$quality)
```

Seeing that this trend presentes itself over more than half of the observations is some additional supporting evidence to the correlation score alcohol and quality have.

Now for the next variable that has a higher correlation to quality, volatile.acidity

```{r echo=TRUE, Bivariate_Plots4}
# http://stackoverflow.com/questions/3989987/joining-means-on-a-boxplot-with-a-line-ggplot2
ggplot(wine_quality, aes(x = quality, y = volatile.acidity)) +
  geom_boxplot() +
  # aes(group = 1) added to line plot forces stat_summary to be scoped to pre-aggregated data so line can connect means from each group
  stat_summary(aes(group = 1), fun.y = mean, geom = "line", show.legend = FALSE) +
  stat_summary(fun.y = mean, geom = "point", shape = "µ", size = 2, show.legend = FALSE) 
```

We can see the the negative correllation clearly here. The IQR is compressing as the quality improves. There is an overall negative trend in volatile.acidity as the quality increases.

Even though the effect of sulphates on quality doesn't rank as highly as some of the other variables, I still want to examine it.

```{r echo=TRUE, Bivariate_Plots5}
# http://stackoverflow.com/questions/3989987/joining-means-on-a-boxplot-with-a-line-ggplot2
ggplot(wine_quality, aes(x = quality, y = sulphates)) +
  geom_boxplot() +
  # aes(group = 1) added to line plot forces stat_summary to be scoped to pre-aggregated data so line can connect means from each group
  stat_summary(aes(group = 1), fun.y = mean, geom = "line", show.legend = FALSE) +
  stat_summary(fun.y = mean, geom = "point", shape = "µ", size = 2, show.legend = FALSE)
```

It would seem that the wines that received a higher score tend to have higher sulphate levels.

The next interesting correllation from the inital corellation plot I want to examine is sulphates by chlorides.

```{r echo=TRUE, Bivariate_Plots6}
ggplot(wine_quality, aes(x = sulphates, y = chlorides)) +
  geom_point(alpha = 1/15)
```

For the majority of the wines sampled the amount of chlorides is fairly consistent except of a few moderate and extreme cases. Sames goes for sulphates except for having the bulk of the values over a slightly larger range. There are observations where the suphate measurement is high and the corresponding chloride measurement is low or high. There are no observations where the suphate measurement is low and the chloride measurement is exteme. I don't think this is a very meanful correllation.

Let's see what a linear model looks like on top of these data.

```{r echo=TRUE, Bivariate_Plots6.1}
ggplot(wine_quality, aes(x = sulphates, y = chlorides)) +
  geom_point(alpha = 1/15) +
  stat_smooth(method = "lm")
```

This was what I was expecting. This doesn't seem to be a meaningful relationship.

There seems to be a fairly strong relationship between volatile.acidity and citric.acid. 

```{r echo=TRUE, Bivariate_Plots7}
ggplot(wine_quality, aes(x = citric.acid, y = volatile.acidity)) +
  geom_point(alpha = 1/10)
```

There is a wide range of volatile.acidity values for each citric.acid measurement. There does seems to be a negative correllation here but the variance would be quite high. The bands of common citric.acid measurements (0.0, 0.24, and 0.49) that were noted during the univariate exploration are visible here. Visually, it seems that beyond citric.acid measurements of 0.49 the trend reverses and begins upward. 

```{r echo=TRUE, Bivariate_Plots8}
ggplot(wine_quality, aes(x = citric.acid, y = volatile.acidity)) +
  geom_point(alpha = 1/10) +
  scale_x_continuous(limits = c(0.3, 1.0), breaks = seq(0.3, 1.0, 0.05))
```

Acctually, the trend seems to be fairly flat from around citric.acid measurements > 0.35.

```{r echo=TRUE, Bivariate_Plots9}
ggplot(wine_quality, aes(x = citric.acid, y = volatile.acidity)) +
  geom_point(alpha = 1/10) +
  scale_x_continuous(limits = c(0.3, 1.0), breaks = seq(0.3, 1.0, 0.05)) +
  stat_smooth(method = "lm")
```

Superimposing a linear model confirms the tendancy is approaching flat but still slightly negative.

The fixed.acidity and citric.acid measurements appear to have a very strong correllation. I was going to ignore this relationship until I read the description of each of the variables again. I was under the impression that the fixed.acidity measurement was a measurement of all acidity except aecetic acid. Since this is not the case let's investigate this relationship.

```{r echo=TRUE, Bivariate_Plots10}
ggplot(wine_quality, aes(x = citric.acid, y = fixed.acidity)) +
  geom_point(alpha = 1/10)
```

Visually, there seems to be an exponential curve. Let's see what log(fixed.acidity) looks like.

```{r echo=TRUE, Bivariate_Plots11}
ggplot(wine_quality, aes(x = citric.acid, y = fixed.acidity)) +
  geom_point(alpha = 1/10) +
  stat_smooth(method = "lm")

ggplot(wine_quality, aes(x = citric.acid, y = log(fixed.acidity))) +
  geom_point(alpha = 1/10) +
  stat_smooth(method = "lm")
```

With the linear model overlayed over the original plot the cure is no longer perceptable. The log(fixed.acidity) plot may have slightly normalized the distribution linearly but it is very difficult to tell. 

At the outset I was expecting alcohol and residual.sugars to be more related than their correllation indicates. Let's have a look at the plot anyway.

```{r echo=TRUE, Bivariate_Plots10}
ggplot(wine_quality, aes(x = alcohol, y = residual.sugar)) +
  geom_point(alpha = 1/20, position = position_jitter(0.01))
```

Here we are reminded of the results from the univariate anaylsis of residual.sugar - most wine having a measurement of 2 g/L.

# Bivariate Analysis

### Talk about some of the relationships you observed in this part of the investigation. How did the feature(s) of interest vary with other features in the dataset?
There seem to be two variable that are driving theo pr varience in the quality variable. Higher acohol content tends toduce better scores. Lower volatile.acidity tends to produce higher scores. There were some other notable and surprising relationships. The sulphate measurements have a mild effect on the quality score. This was something unexpected for me.

### Did you observe any interesting relationships between the other features (not the main feature(s) of interest)?
There is a moderate, negative relationship between the volatile.acidity measurements and the citric.acid measurements. I wasn't expecting these two measurements to be related. Chlorides and Sulfates seems to have a relationship but I am not sure if it is significant. I was expecting alcohol and residual.sugar to have some relationship but they do not. A couple times in areas of certain scatter plots where the density was lower there appeared to be a visually identifiable trend but by adding an additonal visual element to the plot (a linear smoother) these trends usually stopped being perceptable.

### What was the strongest relationship you found?
The strongest relationship I analyzed was between fixed.acidty and citric.acid. This relationship has a 0.7 pearson correlation coeffecient.

# Multivariate Plots Section

```{r echo=FALSE, Multivariate_Plots1}
# http://stackoverflow.com/questions/34975190/set-alpha-and-remove-black-outline-of-density-plots-in-ggpairs
ggscatalpha <- function(data, mapping, ...) {
  ggplot(data = data, mapping = mapping) +
    geom_point(..., alpha = 0.25)
}

ggdensalpha <- function(data, mapping, ...) {
  ggplot(data = data, mapping = mapping) +
    geom_density(..., alpha = 0.25)
}
```

Let's have a look at all the pairs so I know where to spend additional time:

```{r echo=FALSE, Multivariate_Plots2}
wq.names.acid <- c("fixed.acidity", "volatile.acidity", "citric.acid", "pH")
ggpairs(wine_quality,
        columns = wq.names.acid, 
        mapping = aes(color = quality), 
        lower = list(continuous = ggscatalpha), 
        diag = list(continuous = ggdensalpha))
```

```{r echo=FALSE, Multivariate_Plots3}
wq.names.sulphur <- c("free.sulfur.dioxide", "total.sulfur.dioxide", "sulphates", "chlorides")
ggpairs(wine_quality,
        columns = wq.names.sulphur,
        mapping = aes(color = quality),
        lower = list(continuous = ggscatalpha), 
        diag = list(continuous = ggdensalpha))
```

 
```{r echo=FALSE, Multivariate_Plots4}
wq.names.alcohol <- c("alcohol", "residual.sugar", "density")
ggpairs(wine_quality,
        columns = wq.names.alcohol,
        mapping = aes(color = quality),
        lower = list(continuous = ggscatalpha), 
        diag = list(continuous = ggdensalpha))
```

The density plots on the diagonals in the ggpairs plots seem to offer some solid insight so I wanted to try and plot them all at once:

```{r echo=FALSE, Multivariate_Plots6}
# https://stackoverflow.com/questions/14623348/how-to-use-facet-to-create-multiple-density-plot-in-ggplot
# https://stackoverflow.com/questions/18046051/setting-individual-axis-limits-with-facet-wrap-and-scales-free-in-ggplot2
# New favorite function: reshape2::melt :D

wine_quality.m <- melt(wine_quality, id = c("X", "quality"), measure.vars = c("fixed.acidity", "volatile.acidity", "citric.acid", "residual.sugar", "chlorides", "free.sulfur.dioxide", "total.sulfur.dioxide", "density", "pH", "sulphates", "alcohol"))

ggplot(data = wine_quality.m, aes(x = value)) +
  geom_density(aes(color = quality)) + 
  facet_wrap(~variable, scales = "free")
```

That seems to do the trick. In the fixed.acidity plot we can see quality scores of 7 and 8 have a slightly higher mean. In the volatile.acidity plot higher scores have lower means and lower scores have higher means. For citric.acid measurements higher values produce higher scores. In the pH plot we can see a proxy effect reflected in the results from the other acidity related variables. In the suplphates plot we see our higher scoring wines pulling away from the other having a higher mean sulphate measurements. Finally, the alcohol plot illustrates higher scoring wines have higher alcohol content.

First, I'd like to examine volatile.acidity - citric.acid relationship by alcohol content. I will bucket the alcohol varaible in to "Low", "Medium", and "High". "Low" will be alcohol contents between 0 and -1 standard diviation. "Medium" will contain wines with -1 standard diviation to +1 standard diviation alcohol. "High" will represent +1 standard diviation to the max value of the alcohol variable.

```{r echo=FALSE, Multivariate_Plots5}
alcohol.mean <- mean(wine_quality$alcohol)
alcohol.sd <- sd(wine_quality$alcohol)

# Factors the alcohol variable in to Low, Medium, and High buckets for coloring plots
wine_quality$alcohol.buckets <- cut(wine_quality$alcohol, c(0, alcohol.mean - alcohol.sd, alcohol.mean + alcohol.sd, max(wine_quality$alcohol)), labels = c("Low", "Medium", "High"))

ggplot(wine_quality, aes(x = citric.acid, y = volatile.acidity, color = alcohol.buckets)) +
  geom_point(alpha = 0.3) +
  facet_wrap(~quality)
```

Between scores of 5 and 6 we can see the effect of the alcohol variable emmerging. The plots for scores of 5 and 6 have very similar volatile.acidity to citric.acid characteristics, but in the we can see that 6 has several more wines from the 'High' alcohol bucket and fewer from the 'Low' bucket. Examining the highest scores of 7 and 8 we can see the occurance of 'Medium' alcohol bucket observations drop off being replaced with 'High' alcohol obervations. As the score improves we can see that the range of volatile.acidity compresses around the 0.4 measurement. 


```{r echo=FALSE, Multivariate_Plots6}
ggplot(wine_quality, aes(x = citric.acid, y = fixed.acidity, color = alcohol.buckets)) +
  geom_point(alpha = 0.6) +
  facet_wrap(~quality)
```



```{r echo=FALSE, Multivariate_Plots7}
ggplot(wine_quality, aes(x = quality, y = sulphates, color = alcohol.buckets)) +
  #geom_point() +
  geom_jitter(alpha = 0.5)
```

```{r echo=FALSE, Multivariate_Plots8}
m1 <- lm(quality ~ alcohol, data = wine_quality)
m2 <- update(m1, ~ . + volatile.acidity)
m3 <- update(m2, ~ . + fixed.acidity)
m4 <- update(m3, ~ . + sulphates)
m4.1 <- update(m4, ~ . + density)
m4.2 <- update(m4.1, ~ . + pH)
m5 <- update(m4.2, ~ . + total.sulfur.dioxide)
m6 <- update(m5, ~ . + free.sulfur.dioxide)
m7 <- update(m6, ~ . + residual.sugar)
m8 <- update(m7, ~ . + chlorides)
m9 <- update(m8, ~ . + citric.acid)
mtable(m1, m2, m3, m4, m4.1, m4.2, m5, m6, m7, m8, m9)
```

# Multivariate Analysis

### Talk about some of the relationships you observed in this part of the investigation. Were there features that strengthened each other in terms of looking at your feature(s) of interest?

### Were there any interesting or surprising interactions between features?

### OPTIONAL: Did you create any models with your dataset? Discuss the strengths and limitations of your model.

------

# Final Plots and Summary

### Plot One
```{r echo=FALSE, Plot_One}
ggplot(data = wine_quality, aes(x = quality)) + 
  geom_bar(stat = "count", fill = "firebrick") +
  labs(title = "Distribution of Quality Scores", x = "Quality Score", y = "Count") +
  theme(plot.title = element_text(hjust = 0.5), 
        axis.title.x = element_text(size = 14), 
        axis.title.y = element_text(size = 14),
        title = element_text(size = 16))
```

### Description One


### Plot Two
```{r echo=FALSE, Plot_Two}
# http://stackoverflow.com/questions/3989987/joining-means-on-a-boxplot-with-a-line-ggplot2
# https://stackoverflow.com/questions/40675778/center-plot-title-in-ggplot2
ggplot(wine_quality, aes(x = quality, y = alcohol)) +
  geom_boxplot(fill = "firebrick") +
  # aes(group = 1) added to line plot forces stat_summary to be scoped to pre-aggregated data so line can connect means from each group
  stat_summary(aes(group = 1), fun.y = mean, geom = "line", show.legend = FALSE) +
  stat_summary(fun.y = mean, geom = "point", shape = "µ", size = 2, show.legend = FALSE) +
  labs(title = "Alcohol Content by Quality Score", x = "Quality Score", y = "Alcohol (%ABV)") +
  theme(plot.title = element_text(hjust = 0.5), 
        axis.title.x = element_text(size = 14), 
        axis.title.y = element_text(size = 14),
        title = element_text(size = 16))
```

### Description Two


### Plot Three
```{r echo=FALSE, Plot_Three}

```


### Description Three

------

# Reflection
